PANCHANGE_analysis

### 2020-11-09 PANCHANGE_analysis.Rmd

# PCL prepan: sensitivity
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
#### Subset of participants 3 months prior to pandemic
```{r pcl model1b sum_score prepan - sensitivity 3 months}
# Regression coefficients
pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_3months")
kable(pcl_prepan_model1b_explan_estimates)
pcl_prepan_model1b_explan_estimates

>>>>

# SENSITIVITY based on highest level of education

# GAD prepan
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad education sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_estimates)
gad_prepan_model1b_education_estimates

# Regression diagnostic statistics
gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_reg_stats)
gad_prepan_model1b_education_reg_stats
```

# PHQ prepan
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq education sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_estimates)
phq_prepan_model1b_education_estimates

# Regression diagnostic statistics
phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_reg_stats)
phq_prepan_model1b_education_reg_stats
```

# OCIR prepan 
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir education sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_estimates)
ocir_prepan_model1b_education_estimates

# Regression diagnostic statistics
ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_reg_stats)
ocir_prepan_model1b_education_reg_stats
```

#PCL prepan 
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl education sensitivty model1b sum_score prepan}
# Regression coefficients
pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_education_estimates)
pcl_prepan_model1b_education_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_education_reg_stats)
pcl_prepan_model1b_education_reg_stats
```

# SENSITIVITY based on employment status

# GAD prepan
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_employment_estimates)
gad_prepan_model1b_employment_estimates

# Regression diagnostic statistics
gad_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_employment_reg_stats)
gad_prepan_model1b_employment_reg_stats
```

# PHQ prepan
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_employment_estimates)
phq_prepan_model1b_employment_estimates

# Regression diagnostic statistics
phq_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_employment_reg_stats)
phq_prepan_model1b_employment_reg_stats
```

# OCIR prepan 
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir employment sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_employment_estimates)
ocir_prepan_model1b_employment_estimates

# Regression diagnostic statistics
ocir_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_employment_reg_stats)
ocir_prepan_model1b_employment_reg_stats
```

#PCL prepan 
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl employment sensitivty model1b sum_score prepan}
# Regression coefficients
pcl_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_employment_estimates)
pcl_prepan_model1b_employment_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_employment_reg_stats)
pcl_prepan_model1b_employment_reg_stats
```

# SENSITIVITY based on employment change

```{r create an employment change variable}
dat.prepan <- dat.prepan %>%
  mutate(employment_change =
           case_when(
             employment.unemployed_numeric == "1" ~ "Unemployed",
             employment.became_unemployed_numeric == "1" ~ "Became Unemployed",                         
             employment.furloughed_or_paid_leave_government_funded_numeric == "1" ~ "Furlough",
             employment.furloughed_or_paid_leave_company_funded_numeric == "1" ~ "Furlough",    
             employment.paid_leave_furloughed_numeric == "1" ~ "Furlough",                             
             key_worker_numeric == "1" ~ "Key Worker",                                            
             employment.government_work_key_workers_numeric == "1" ~ "Key Worker",                
             employment.zerohours_contract_numeric == "1" ~ "Zero Hours Contract",                         
             employment.retired_numeric == "1" ~ "Retired",                                   
             employment.student_gcse_or_a_level_numeric == "1" ~ "Student",                   
             employment.student_university_numeric == "1" ~ "Student"                        
           )
  )

dat.prepan$employment_change <- as.factor(dat.prepan$employment_change)
```

# GAD prepan
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment change sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "employment_change",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_employmentchange_estimates)
gad_prepan_model1b_employmentchange_estimates

# Regression diagnostic statistics
gad_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "employment_change",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_employmentchange_reg_stats)
gad_prepan_model1b_employmentchange_reg_stats
```

# PHQ prepan
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment change sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "employment_change",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_employmentchange_estimates)
phq_prepan_model1b_employmentchange_estimates

# Regression diagnostic statistics
phq_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "employment_change",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_employmentchange_reg_stats)
phq_prepan_model1b_employmentchange_reg_stats
```

# OCIR prepan 
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir employment change sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "employment_change",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_employmentchange_estimates)
ocir_prepan_model1b_employmentchange_estimates

# Regression diagnostic statistics
ocir_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "employment_change",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_employmentchange_reg_stats)
ocir_prepan_model1b_employmentchange_reg_stats
```

#PCL prepan 
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl employment change sensitivty model1b sum_score prepan}
# Regression coefficients
pcl_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "employment_change",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_employmentchange_estimates)
pcl_prepan_model1b_employmentchange_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "employment_change",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_employmentchange_reg_stats)
pcl_prepan_model1b_employmentchange_reg_stats
```

# Sensitivity based on GLAD sign up
#PCL prepan: sensitivity
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
#### Subset of participants 3 months prior to pandemic
```{r pcl model1b sum_score prepan - sensitivity 3 months}
# Regression coefficients
pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_3months")
kable(pcl_prepan_model1b_explan_estimates)
pcl_prepan_model1b_explan_estimates
